Supporting Information for: \\ Large scale risks from agricultural pesticides in small streams

### 2017-06-04 supplement/Supplemental_Materials.tex
final draft of revision

\usepackage[
	round,	%(defaultage in the main file and \input ) for round parentheses;
	authoryear,% (default) for author-year citations;
	sort,		% orders multiple citations into the sequence in which they 
]{natbib}

@@

\bibliographystyle{spbasic}      % basic style, author-year citations
\bibliography{references}

>>>>

\usepackage[
	round,	%(defaultage in the main file and \input ) for round parentheses;
	numbers,
	sort,		% orders multiple citations into the sequence in which they 
]{natbib}	
\renewcommand{\bibname}{References}

@@

\bibliographystyle{plainnat}      
\bibliography{references}
